\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2015-10-15 tex/paper.tex
Changed snapshot definition

\clearpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Introduction}
Developing larger projects containing static content usually involves using a Content Distribution Network 
to be able to scale to a large user base. The commercial Content Distribution Networks are usually fairly easy to use, 
the content that is to be used in a project is usually simply uploaded and then directly available to the public. 
For secret content this can be a problem and that is what this thesis is about. This work examines ways of enforcing 
access control on content and groups of content in the form of views. A system was developed to make the underlying 
theory work in practice.

@@

\subsubsection{CDN}
Content Distribution Network - Replicates content to several servers, usually spread out geographically. Once a 
request is made, the network serves content from the server closest to the requester.

@@

\subsection{The current system}
Maybe write about battlebinary?

\subsection{Problem description}
Having

Battle Binary

What is needed
* Security layers
* Views
* Virtual file structure
* Versioning of content
* Multi project support
* Auth and audit logs
* Users
\newpage 
\section{Model}
\subsection{Entities}
%\subsubsection*{View} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{Entity Relationships}
    \label{fig:relation}
\end{figure}

\subsubsection{Content}
Content is an asset contained in a project and/or view, it is a form of virtual file.
It could be described as a link between the view or project and the real file. 
    The content can be for example an image, video or binary blob, combined with meta-data.

\subsubsection{Project}
A project is what is created to contain all content related to a real project. Files can be changed within a project and 
the system can contain several projects and their virtual content are completely disjoint.

\subsubsection{View}
A view is a subset of content, in a project, from the state which they were in when the view was created. A project can 
contain many views. A view can have content which either is automatically dependant on its parent project and updated 
when the parent is updated or stay in the state which it was in when the view was created. This results in that the content 
within a view can not be updated independently from its project.

\subsubsection{Folder}
A folder is a virtual folder within the projects which contains content.

@@

\subsection{JPF}
Java path finder was used to show that the model and plan of how to build the system was sound. The model was built in Java 
with the objective of being as reduced and simple as possible, without loosing any of the cases that needs to be covered 
by the model checker.

@@

@@

  \item projects/\{id\}/views
      \subitem GET - list all views in a specific project
      \subitem POST - create new view in a specific project 
  \item projects/\{id\}/views/\{id\}
      \subitem GET - get specific view in a specific project
      \subitem PUT - update existing view
      \subitem DELETE - delete existing view
  \item projects/\{id\}/views/\{id\}/content
      \subitem GET - list all content in a specific view
      \subitem POST - create new content in a specific view 
  \item projects/\{id\}/views/\{id\}/content/\{id\}
      \subitem GET - get specific content in a specific view
      \subitem PUT - update existing content in a specific view
      \subitem DELETE - delete existing content in a specific view

  \item projects/\{id\}/folders
      \subitem GET - list all folders in a specific project
      \subitem POST - create new folder in a specific project 
  \item projects/\{id\}/folder/\{id\}
      \subitem GET - get specific folder in a specific project
      \subitem PUT - update existing folder
      \subitem DELETE - delete existing folder
  \item projects/\{id\}/folder/\{id\}/content
      \subitem GET - list all content in a specific folder
      \subitem POST - create new content in a specific folder 
  \item projects/\{id\}/folder/\{id\}/content/\{id\}
      \subitem GET - get specific content in a specific folder
      \subitem PUT - update existing content in a specific folder
      \subitem DELETE - delete existing content in a specific folder
\end{itemize}

>>>>

\clearpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Introduction}
Developing larger projects containing static content usually involves using a Content Distribution Network 
to be able to scale to a large user base. The commercial Content Distribution Networks are usually fairly easy to use, 
the content that is to be used in a project is usually simply uploaded and then directly available to the public. 
For secret content this can be a problem and that is what this thesis is about. This work examines ways of enforcing 
access control on content and groups of content in the form of snapshots. A system was developed to make the underlying 
theory work in practice.

@@

\subsubsection{CDN}
Content Distribution/Delivery Network - Replicates content to several servers, usually spread out geographically. Once a 
request is made, the network serves content from the server closest to the requester.

@@

\subsection{The current system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files, mostly images, to content 
delivery networks. The current system does not make use out of the security features that the CDN's are offering, instead it 
uses a form of security by obscurity. When a file is uploaded to a CDN it is open for the public, but its filename is 
composed out of its original filename concatenated with a part of the MD5 hash of the content of the file, which makes it an 
extremely hard process to access the file on the CDN without access to the original file or a reference to the URI.

In the current system you can only upload a file once as there will be a collision in the upload otherwise, as the old and 
the new file will have the same MD5 hash.

\subsection{Problem description}
As the current system does not offer proper security measurements, is lacking a lot of features that is needed and does not 
scale very well, a new system should be developed. This work is about examining a way of implementing Copy-on-Write in a 
high level system, which should solve the scalability problem and makes it possible to implement the wanted features, like 
snapshots and concurrent modifications of content.

What to write about
Battle Binary
Security features of CDN's

What is needed
* Security layers
* snapshots
* Virtual file structure
* Versioning of content
* Multi project support
* Auth and audit logs
* Users
\newpage 
\section{Model}
\subsection{Entities}
%\subsubsection*{snapshot} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{Entity Relationships}
    \label{fig:relation}
\end{figure}

\subsubsection{Content}
Content is an asset contained in a project and/or snapshot, it is a form of virtual file.
It could be described as a link between the snapshot or project and the real file. 
The content can be for example an image, video or binary blob, combined with meta-data.

\subsubsection{Project}
A project is what is created to contain all content related to a real project. Files can be changed within a project and 
the system can contain several projects and their virtual content are completely disjoint.
snapshot
\subsubsection{Snapshot}
A snapshot is a read-only container from the state which the container the was in when the snapshot was created. A snapshot can 
have content which either is automatically dependant on the container which it was created from and updated when that container 
is updated or stay in the state which it was in when the snapshot was created. This results in that the content within a snapshot 
can not be updated independently from the container which it was created from.

\subsubsection{Container}
A container is a virtual folder within the projects which contains content and other containers.

@@

\subsection{JPF}
Java path finder was used to show that the model and plan of how to build the system was sound. The model was built in Java 
with the objective of being as reduced and simple as possible, without loosing any of the cases that needs to be covered 
by the model checker. As the users are mainly going to be handled by external systems they were not included in the model.

@@

ConcurrentHashMap had to be used in favour of the normal HashMap as the normal HashMaps can't be iterated over concurrently.

@@

  \item projects/\{id\}/snapshots
      \subitem GET - list all snapshots in a specific project
      \subitem POST - create new snapshot in a specific project 
  \item projects/\{id\}/snapshots/\{id\}
      \subitem GET - get specific snapshot in a specific project
      \subitem PUT - update existing snapshot
      \subitem DELETE - delete existing snapshot
  \item projects/\{id\}/snapshots/\{id\}/content
      \subitem GET - list all content in a specific snapshot
      \subitem POST - create new content in a specific snapshot 
  \item projects/\{id\}/snapshots/\{id\}/content/\{id\}
      \subitem GET - get specific content in a specific snapshot
      \subitem PUT - update existing content in a specific snapshot
      \subitem DELETE - delete existing content in a specific snapshot

  \item projects/\{id\}/containers
      \subitem GET - list all containers in a specific project
      \subitem POST - create new container in a specific project 
  \item projects/\{id\}/containers/\{id\}
      \subitem GET - get specific container in a specific project
      \subitem PUT - update existing container
      \subitem DELETE - delete existing container
  \item projects/\{id\}/containers/\{id\}/content
      \subitem GET - list all content in a specific container
      \subitem POST - create new content in a specific container 
  \item projects/\{id\}/containers/\{id\}/content/\{id\}
      \subitem GET - get specific content in a specific container
      \subitem PUT - update existing content in a specific container
      \subitem DELETE - delete existing content in a specific container
\end{itemize}
